---
title: "Cell-type specific mediation project update"
author: "Andrea Lane"
date: "6/8/2021"
output: 
   pdf_document:
        toc: true
        extra_dependencies: ["amsmath", "xcolor","bm"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(kableExtra)
library(stringr)
library(ROCR)
library(PRROC)
```
 
\newpage

\section{Method derivation}


The equation 6 and 7 in HIRE can be written using our notations as
\begin{align*}
M~&\sim~ N(\sum_{k = 1}^{K}m_{k}\pi_{k}, \sigma^2) \\
m_{k}~&\sim~N(\beta_0^k + \beta_1^k E, \tau_{k}^2)
\end{align*}

Our current model is
 \begin{align*}
& E[Y] = \theta_0 + \theta_1 E + \sum_k \theta_2^k m_{k} \\
& E[m_{k}]  = \beta_0^k + \beta_1^k E
\end{align*}

To use GEM to solve our model in the similar way as HIRE, write our problem as
\begin{align*}
Y~&\sim~ N(\theta_0 + \theta_1 E + \sum_k \theta_2^k m_{k}, ~\gamma^2)\\
M~&\sim~ N(\sum_{k}m_{k}\pi_{k}, ~\sigma^2) \\
m_{k}~&\sim~N(\beta_0^k + \beta_1^k E, ~\tau_{k}^2)
\end{align*}

We can employ the generalized expectation-maximization (GEM) algorithm in the similar way as HIRE. After augmenting the missing data $\bm{\mathcal{M}} = \{m_{k} : 1 \le k \le K\}$ to the observed data, the complete-data log-likelihood function has a tractable form:
\begin{align*}
l_c(\mathbf{\Theta} | \mathbf{Y}, \mathbf{E}, \bm{M}, \bm{\mathcal{M}}, \bm{\pi}) = \sum_{i = 1}^{n} \big[& -\frac{1}{2} log \sigma^{2} - \frac{(M_i - \sum_{k} m_{ik}\pi_{ik})^2}{2\sigma^2} \\
& - \frac{1}{2} \sum_{k} log\tau_{k}^2 - \sum_k \frac{(m_{ik} - \beta_0^{k} - \beta_1^{k} E_i)^2}{2\tau_{ik}^2} \\
&- \frac{1}{2}log \gamma^2 - \frac{(Y_i - \theta_0 - \theta_1 E_{i} - \sum_k \theta_2^{k}m_{ik})^2}{2\gamma^2}\big].
\end{align*}
Here $\mathbf{\Theta} ~=~ \{\bm{\beta},\bm{\theta}, \tau_{k}^2, \sigma^2, \gamma^2: 1 \le k \le K \}$. Estimate $\bm{\mathcal{M}}$ using E-step and $\bm{\Theta}$ using M-step.

Note that the above derivation assumes outcome $Y$ follows normal distribution. This may not hold in many situations. For example in the RA data, we use a binary variable, developed RA or not, as the outcome. For these cases, we could adopt a genelized linear model frame work. Adding an additional layer to the above model
\begin{align*}
Y|\mu_{Y} ~&\sim~ F(y; \mu_Y)\\
g(\mu_Y)~&\sim~ N(\theta_0 + \theta_1 E + \sum_k \theta_2^k m_{k}, ~\gamma^2)\\
M~&\sim~ N(\sum_{k}m_{k}\pi_{k}, ~\sigma^2) \\
m_{k}~&\sim~N(\beta_0^k + \beta_1^k E, ~\tau_{k}^2)
\end{align*}
where $\mu_Y = E(Y)$ and $g(\cdot)$ is the link function. $F(\cdot)$ is the CDF of the distribution of interest, e.g. Bernoulli distribution. 

\newpage 

\textbf{E-M derivation}:

E-step:

\begin{align*}
\sum_{i=1}^{n} -\frac{1}{2} log \sigma^{2(t)} - \frac{E[(M_i - \sum_{k} m_{ik}\pi_{ik})^2 | Y_i, M_i, E_i, \Theta]}{2\sigma^{2(t)}}\\
-\frac{1}{2}\sum_klog\tau_{k}^{2(t)}-\sum_k\frac{E[(m_{ik}-\beta_0^k-\beta_1^kE_i)^2 | Y_i, M_i, E_i, \Theta]}{2\tau_{k}^{2(t)}}\\
-\frac{1}{2}log \gamma^{2(t)} -\frac{1}{2\gamma^{2(t)}}E[(Y_i - \theta_0 - \theta_1 E_{i} - \sum_k \theta_2^{k}m_{ik})^2 | Y_i, M_i, E_i, \Theta]
\end{align*}

To calculate these expectations, we need $f(m_{ik} | Y_i, E_i, M_i, \Theta)$

\begin{align*}
f(m_{ik} | Y_i, E_i, M_i, \Theta) \propto f(Y_i | E_i, M_{ik}; \Theta)f(M_i | m_{ik}, \pi_{ik}; \Theta)f(m_{ik} | E_i; \Theta) \\
\propto e^{\frac{-(y_i-\theta_0^{(t)}-\theta_1^{(t)}E_i-m_i^T\theta_2^{(t)})^2}{2\gamma^{(t)2}}}e^{\frac{-(M_i-m_i^T\pi_i)^2}{2\sigma^{(t)2}}}e^{-\frac{1}{2}(m_i-\beta^{(t)}_0-\beta^{(t)}_1E_i)^T\Sigma^{(t)-1}(m_i-\beta_0^{(t)}-\beta_1^{(t)}E_i)}
\end{align*}

where $m_i = (M_{i1},...,M_{iK})^T$, $\beta_0$, $\beta_1$, $\pi_i$ and $\theta_2$ are k-length vectors, and $\Sigma = diag(\tau_1^2 ... \tau_k^2)$

Following HIRE, we can combine these in this form:

\begin{align*}
\propto e^{-\frac{1}{2}\big[m_i^T(\frac{\theta_2^{(t)}\theta_2^{(t)T}}{\gamma^{(t)2}}+\frac{\pi_i\pi_i^T}{\sigma^{(t)2}}+\Sigma^{(t)-1})m_i-2(\frac{(y_i-\theta_0^{(t)}-\theta_1^{(t)}E_i)\theta_2^{(t)T}}{\gamma^{(t)2}}+\frac{M_i\pi_i^T}{\sigma^{(t)2}}+(\beta_0^{(t)}+\beta_1^{(t)}E_i)^T\Sigma^{(t)-1})m_i\big]}
\end{align*}

Therefore, the conditional distribution of $m_i$ is $N(\mu_{i*}^{(t)},\Sigma_{i*}^{(t)})$, where $\Sigma_{i*}^{(t)-1} := \frac{\theta_2^{(t)}\theta_2^{(t)T}}{\gamma^{(t)2}}+\frac{\pi_i\pi_i^T}{\sigma^{(t)2}}+\Sigma^{(t)-1}$ and $\mu_{i*}^{(t)}\Sigma_{i*}^{(t)-1} := \frac{(y_i-\theta_0^{(t)}-\theta_1^{(t)}E_i)\theta_2^{(t)T}}{\gamma^{(t)2}}+\frac{M_i\pi_i^T}{\sigma^{(t)2}}+(\beta_0^{(t)}+\beta_1^{(t)}E_i)^T\Sigma^{(t)-1}$. Note that $\mu_{i*}$ is a k-length vector and $\Sigma_{i*}$ is a kxk matrix

So then

\begin{align*}
E[(M_i - \sum_{k} m_{ik}\pi_{ki})^2 | Y_i, M_i, E_i, \pi_i, \Theta] = \pi_i^T\Sigma_{i*}^{(t)}\pi_i + (M_i-\mu_{i*}^{(t)T}\pi_i)^2
\end{align*}

\begin{align*}
E[(Y_i - \theta_0 - \theta_1 E_{i} - \sum_k \theta_2^{k}m_{ik})^2 | Y_i, M_i, E_i, \pi_i, \Theta] = \theta_2^T\Sigma_{i*}^{(t)}\theta_2 + (Y_i - \theta_0 - \theta_1 E_{i}-\mu_{i*}^{(t)T}\theta_2)^2
\end{align*}

and 

\begin{align*}
E[(m_i-\beta_0-\beta_1E_i)^T\Sigma^{-1}(m_i-\beta_0-\beta_1E_i)| Y_i, M_i, E_i, \pi_i, \Theta] \\
= (\mu_{i*}^{(t)}-\beta_0-\beta_1E_i)^T\Sigma^{-1}(\mu_{i*}^{(t)}-\beta_0-\beta_1E_i)+\sum_k\frac{\sigma_{i*,kk}^{(t)2}}{\sigma^2_{k}}
\end{align*}

where $\sigma_{i*,kk}^{(t)2}$ is the kth diagonal element of $\Sigma_{i*}^{(t)}$

M-step:

Using the general form of derivitive of quadratic form, $\frac{d}{dx}x^TAx=x^T(A+A^T)$, we have

\begin{align*}
\frac{dE[l_c]}{d\beta_0^k} = \sum_{i=1}^{n} -(\mu_{i*}^{(t)}-\beta_0^k-\beta_1^kE_i)^T(\Sigma^{-1}+\Sigma^{-1T}) := 0\\
\implies \sum_{i=1}^{n} \mu_{*}^{(t)} - \sum_{i=1}^{n} \beta_0^k - \sum_{i=1}^{n} \beta_1^kE_i = 0 \\
\implies n\beta_0^k = \sum_{i=1}^{n} (\mu_{i*}^{(t)}-\beta_1^kE_i) \\
\implies \beta_0^{k(t+1)} = \frac{\sum_{i=1}^{n} (\mu_{i*}^{(t)}-\beta_1^{k(t)}E_i)}{n}
\end{align*}

Similarly, we have

\begin{align*}
\beta_1^{k(t+1)} = \frac{\sum_{i=1}^n (\mu_{i*}^{(t)}-\beta_0^{k(t+1)})E_i}{\sum_{i=1}^{n}E_i^2}
\end{align*}

\begin{align*}
\theta_0^{(t+1)} = \frac{\sum_{i=1}^{n} (Y_i - \theta_1^{(t)}E_i - \sum_k(\mu_{i*}^{k(t)}\theta_2^{k(t)}))}{n}
\end{align*}

\begin{align*}
\theta_1^{(t+1)} = \frac{\sum_{i=1}^{n} (Y_i - \theta_0^{(t+1)} - \sum_k\mu_{i*}^{k(t)}\theta_2^{k(t)})E_i}{\sum_{i=1}^n E_i^2}
\end{align*}


\begin{align*}
\frac{dE[l_c]}{d\theta_2} = \sum_{i=1}^n \frac{-1}{2\gamma^{2(t)}}\big[\theta_2^T(\Sigma_{i*}^{(t)}+\Sigma_{i*}^{(t)T})-2(Y_i-\theta_0-\theta_1E_i)\mu_{i*}^{(t)}+2\theta_2^T\mu_{i
*}^{(t)}\mu_{i*}^{(t)T})\big]:=0\\
\implies \theta_2^{T(t+1)} = \sum_{i=1}^n (Y_i-\theta_0^{(t+1)}-\theta_1^{(t+1)}E_i)\mu_{i*}^{(t)}(\sum_{i=1}^n \Sigma_{i*}^{(t)}+\mu_{i*}^{(t)}\mu_{i*}^{(t)T})^{-1}
\end{align*}

\begin{align*}
\sigma^{2(t+1)} = \frac{\sum_{i=1}^n \pi_i^T\Sigma_{*}^{(t)}\pi_i + (M_i-\mu_{i*}^{(t)T}\pi_i)^2}{n}
\end{align*}

\begin{align*}
\gamma^{2(t+1)} = \frac{\sum_{i=1}^n \theta_2^{(t+1)T}\Sigma_{i*}^{(t)}\theta_2^{(t+1)} + (Y_i-\theta_0^{(t+1)}-\theta_1^{(t+1)}E_i-\mu_{i*}^{(t)T}\theta_2^{(t+1)})^2}{n}
\end{align*}

\begin{align*}
\tau_k^{2(t+1)} = \frac{\sum_{i=1}^n [(\mu_{i*}^{(t)}-\beta_0^{k(t+1)}-\beta_1^{k(t+1)}E_i)^2+\sigma_{i*,kk}^{2(t+1)}]}{n}
\end{align*}

Following HIRE, we will calculate the observed log-likelihood to assess convergence.

\begin{align*}
Y~\sim~ N(\theta_0+\theta_1E+\sum_k\theta_2^k(\beta_0^k+\beta_1^kE),\sum_k\theta_2^{k2}\tau_k^2+\gamma^2) \\
M~\sim~ N(\sum_k\pi_k(\beta_0^k+\beta_1^kE),\sum_k\pi_k^2\tau_k^2+\sigma^2) \\
l_o(\Theta | Y, M, \Pi) = \sum_{i=1}^{n} log N(Y) + log N(M) \\
\end{align*}

where $N(Y)$ and $N(M)$ indicate the normal density evaluated with the above means and variances. Note that $\pi_k$ depends on $i$, so the variance of $M$ is different for each $i$, while the variance of $Y$ is the same for each $i$.

\newpage

\section{Simulation Setup}

**Data generation**:

 - Binary exposure vector, 50% exposed and 50% unexposed
 - Cell-type-specific methylation values generated from beta distribution using BloodPureDNAmethy_4ct.rda values for mean and sd. Specifically, mean and sd are used to backsolve for alpha and beta, which are then used to generate true methylation values from a beta distribution. Sites selected by sampling from those with mean between 0.4 and 0.6.
  - exposure-mediator effect induced by adding $\beta_1$ to cell-type-specific methylation value in exposed subjects/ $\beta_1$ randomly generated from Unif(0.1,0.4)
 - after adding the mediation effect $\beta_1$, methylation values are checked to be sure they are between 0 and 1: any values $>1$ are set to 0.99 and any values $<0$ are set to 0.01.
 - cell type proportions generated from dirichlet distribution with the following alpha values:
     + 2 cells: 0.4, 0.6
     + 3 cells: 0.2, 0.3, 0.5
     + 4 cells: 0.1, 0.2, 0.3, 0.4
 - Direct effect selected from Unif(0.01,0.05)
 - mediator-outcome effect induced by taking the sum of the cell-type-specific methylation values times $\theta_2$ across all mediating sites (in these results, we only have one mediating site). $\theta_2$ randomly generated from Unif(0.1,0.4)
 - $\gamma = SD(Y_1)$/gamma denominator, where $Y_1$ is the originally generated outcome. The gamma denominator is either 2 or 5, which results in $\gamma \approx 0.01$ or $\gamma \approx 0.004$, respectively.
 - $\tau_k$ taken from BloodPureDNAmethy_4ct.rda
 - $\sigma = 0.03, 0.05, 0.1$ (only results for 0.03 and 0.1 are shown in this document)

**EM**:

 - EM is used to obtain parameter estimates. Percentile bootstrap is used to determine mediating sites/cell types.
  - max.iter=500 and tol=0.001
  - EM initial values:
     + $\beta_0, \beta_1$: coefficients from TOAST
     + tau, sigma, gamma: sampled from inverse gamma distribution with mean 0.001 (based on HIRE, which states that variance initial values are sampled from inverse gamma distribution with small mean but does not specify the mean)
     + $\theta_0, \theta_1: 0$
     + $\theta_2$: 3 cases
          1. EM - True: true values
          2. EM - random: random value generated from normal distribution with mean 0.3 (approx. mean of Y), SD 0.05 for each cell type
          3. EM - TOAST: The model $M \sim Y + E$ is fit with TOAST. For significant cell types, the mean of the outcome is used as the initial value. For non-significant cell types, the initial value is 0.
          4. EM - Hybrid: The model $M \sim Y + E$ is fit with TOAST. For significant cell types, the mean of the outcome is used as the initial value. For non-significant cell types, the initial value is a random value generated from normal distribution with the mean of the outcome as the mean and the SD of the outcome as the SD. 
  - To calculate the p-value, I took the minimum of (1) the number of bootstrap indirect effect estimates $>$ 0, and (2) the number of bootstrap indirect effect estimates $<$ 0, divided this number by the number of bootstrap samples, and multiplied by 2. To assesss significance, I used .05/Number of cell types

                
**Competing methods**:

 - TCA: TCA is used to find estimates of $m_k$, the cell-type-specific methylation values. The models $m_k \sim E$ and $Y \sim E+m_k$ are then fit. The product of coefficients $\hat{\beta_1}\hat{\theta_2}$ is calculated for each cell type, and percentile bootstrap is used to determine significance. The same multiple testing correction is used as in EM.
 - MICS: The MICS package is used to detect mediating cell types. The package requires covariates, so a covariate vector is generated from $N(0,1)$


```{r functions, echo=FALSE, message=FALSE}
setwd("/Users/andrealane/Dropbox/CelltypeSpecificMediation/Simulation/dissertation/")

getmat <- function(method, initval, Nsam, Ncell, medpi){
        mat <- matrix(0,nrow=ifelse(method=="EM",1,2),ncol=Ncell)
        for(i in 1:10){
                new <- read.table(paste0("Report_032821/",method,"_",initval,"_N",Nsam,
                                         "_Ncell",Ncell,"_medpi",medpi,"_",i))
                mat <- mat + new
        }
        return(mat)
}


gettabmat <- function(Nsam,Ncell){
        tabmat <- matrix(0,nrow=1,ncol=Ncell)
        for(i in 1:Ncell){
                tabmat <- rbind(tabmat,
                getmat("EM","true",Nsam,Ncell,i),
                getmat("EM","rand",Nsam,Ncell,i),
                getmat("EM","toast",Nsam,Ncell,i),
                getmat("Comp","true",Nsam,Ncell,i)
                )
        }
        return(tabmat[-1,])
}

getpvalmat <- function(folder,Ncell,medpi,Nsam,method,sigma,tau,gammadenom,alpha=.05){
  mymat <- c()
    for(j in 1:10){
      newmat <- as.matrix(read.table(paste0(folder,"/",method,"_N",Nsam,"_Ncell",Ncell,"_medpi",medpi,"_sigma",sigma,"_tau",tau,"_gammadenom",gammadenom,"_iseed",j)))
      #if(method=="MICS_Pvals"){newmat <- t(newmat)}
      #newmat <- as.numeric(newmat)
      mymat <- rbind(mymat,newmat)
    }
  myalpha <- ifelse(method=="MICS_Pvals",0.05,alpha)
  binmat <- ifelse(mymat<myalpha,1,0)
  return(list(mymat=mymat,binmat=binmat))
}

getlabmat <- function(Ncell,medpi){
  mat <- matrix(1,100,Ncell)
  mat[,medpi] <- 0
  return(mat)
}

makeroc <- function(folder,Ncell,medpi,Nsam,sigma,tau,gammadenom=2,leg=FALSE,title,type="roc",nmethod=3){
  colvec <- c("#E69F00", "#56B4E9", "#009E73", 
                       "#0072B2", "#D55E00", "#CC79A7")
  
  pvals1 <- getpvalmat(folder,Ncell,medpi,Nsam,"EM_hybridPvals",sigma,tau,gammadenom)$mymat
  pvals2 <- getpvalmat(folder,Ncell,medpi,Nsam,"TCA_Pvals",sigma,tau,gammadenom)$mymat
  pvals3 <- getpvalmat(folder,Ncell,medpi,Nsam,"MICS_Pvals",sigma,tau,gammadenom)$mymat
  pvals3 <- ifelse(pvals3==1,0.99,pvals3)
  pvals4 <- if(nmethod==4 | nmethod==5){getpvalmat(folder,Ncell,medpi,Nsam,"EM_toastPvals",sigma,tau,gammadenom)$mymat}
  pvals5 <- if(nmethod==5){getpvalmat(folder,Ncell,medpi,Nsam,"EM_truePvals",sigma,tau,gammadenom)$mymat}
  labmat <- getlabmat(Ncell,medpi)
  
  pred1 <- prediction(as.numeric(pvals1),as.numeric(labmat))
  pred2 <- prediction(as.numeric(pvals2),as.numeric(labmat))
  pred3 <- prediction(as.numeric(pvals3),as.numeric(labmat))
  pred4 <- if(nmethod==4 | nmethod==5){prediction(as.numeric(pvals4),as.numeric(labmat))}
  pred5 <- if(nmethod==5){prediction(as.numeric(pvals5),as.numeric(labmat))}

  if(type=="pr"){
  perf1 <- performance(pred1,measure="prec",x.measure="rec")
  perf2 <- performance(pred2,measure="prec",x.measure="rec")
  perf3 <- performance(pred3,measure="prec",x.measure="rec")
  perf4 <- if(nmethod==4 | nmethod==5){performance(pred4,measure="prec",x.measure="rec")}
  perf5 <- if(nmethod==5){performance(pred5,measure="prec",x.measure="rec")}
  xlims <- c(0,1)
  }
  if(type=="roc"){
  perf1 <- performance(pred1,measure="tpr",x.measure="fpr")
  perf2 <- performance(pred2,measure="tpr",x.measure="fpr")
  perf3 <- performance(pred3,measure="tpr",x.measure="fpr")
  perf4 <- if(nmethod==4 | nmethod==5){performance(pred4,measure="tpr",x.measure="fpr")}
  perf5 <- if(nmethod==5){performance(pred5,measure="tpr",x.measure="fpr")}
  xlims=c(0,1)
  }
  #rocplot <- plot(perf1, col=colvec[1],
   #               main=title,xaxt="n",yaxt="n", lwd=3, cex.main=2, cex.lab=1.4)
  rocplot <- plot(perf1, col=colvec[1],
                  main=title,xaxt="n",yaxt="n",xlim = xlims,ylim=c(0,1))

            plot(perf2, add = TRUE, col=colvec[2],yaxt="n",xaxt="n")
            plot(perf3, add = TRUE, col=colvec[3],yaxt="n",xaxt="n")
            if(nmethod==4 | nmethod==5){plot(perf4, add=TRUE, col=colvec[4],yaxt="n",xaxt="n")}
            if(nmethod==5){plot(perf5, add=TRUE, col=colvec[5],yaxt="n",xaxt="n")}
            if(leg && nmethod==3){legend("bottomright",legend=c("EM","TCA","MICS"),col=colvec[1:3],lty=1)}
            if(leg && nmethod==4){legend("bottomright",legend=c("EM-H","TCA","MICS","EM-To"),col=colvec[1:4],lty=1)}
           if(leg && nmethod==5){legend("bottomright",legend=c("EM-H","TCA","MICS","EM-To","EM-Tr"),col=colvec[1:5],lty=1)}
           if(type=="roc"){abline(a=0, b= 1)}

  return(rocplot)
}

type1tab <- function(tabmat,nmethod){
        Ncell <- ncol(tabmat)/3
        mytab <- matrix(NA,nrow=nmethod*Ncell,ncol=3)
        for(i in 1:3){ #loop over sample sizes
                for(j in 1:Ncell){ #loop over mediating cells
                       mytab[(nmethod*(j-1))+(1:nmethod),i] <- rowMeans(tabmat[,(i-1)*(Ncell)+(1:Ncell)][(nmethod*(j-1))+(1:nmethod),-j]) 
                }
        } 
        return(mytab/100)
}

type1plot <- function(Nsam,Ncell,tabmat,nmethod=6,text=FALSE,ylab=FALSE,xlab=FALSE,yax=FALSE,title=FALSE,leg=FALSE){
        colvec <- c("#E69F00", "#56B4E9", "#009E73", 
                       "#0072B2", "#D55E00", "#CC79A7") #colorblind friendly
        pchvec <- 0:5
        colvec <- if(nmethod==4) {colvec[-2]} else {colvec}
        pchvec <- if(nmethod==4) {pchvec[-2]} else {pchvec}
        y <- ifelse(Nsam==1000,3,ifelse(Nsam==500,2,1))
        y.lim <- ifelse(nmethod==4,0.4,1)
        plotvec <- c()
        for(i in 1:Ncell){
                plotvec <- cbind(plotvec,
                      tabmat[i*nmethod-(nmethod-1),y])
        }
        myplot <- plot(as.vector(plotvec),type="b",xlim=c(0.5,Ncell+0.5),
             ylim=c(0,y.lim),col=colvec[1],pch=pchvec[1],
             xlab="",
             ylab="",xaxt="n",yaxt="n")
        #if(text) text(0.85,tabmat[1,1+y.add]-7,str_replace_all(substr(rownames(tabmat)[1],1,7)," ",""))
        for(i in 1:(nmethod-1)){
                plotvec2 <- c() 
                        for(j in 1:Ncell){
                                plotvec2 <- cbind(plotvec2,
                                tabmat[(i+j)+((j-1)*(nmethod-1)),y])
                        }
                lines(as.vector(plotvec2),
                      type="b",col=colvec[i+1],pch=pchvec[i+1])
                #if (text) text(c(0.7,0.7,0.8,0.8)[i],c(96, 55,12,3)[i],str_replace_all(substr(rownames(tabmat)[i+1],1,7)," ",""))
        }
        axis(1,at=1:Ncell,labels = TRUE,tck=0,padj=-1.8)
        if(yax) axis(2,at=c(0.05,y.lim),labels = TRUE,tck=0,las=2, mgp=c(3, .2, 0))
        if(ylab) title(ylab="Type 1 Error", line=1)
        if(xlab) title(xlab="Mediating Cell", line=1)
        mymain <- ifelse(Nsam==200,"N=200",ifelse(Nsam==500,"N=500","N=1000"))
        if(title) title(main=mymain,line=0.2,font.main=1)
        abline(h=0.05,col="black")
        if(leg && nmethod==6) legend(0.4,1.05,legend=c("EM-Tr","EM-Ra","EM-H","EM-TO",
                                                       "TCA","MICS"),
                       col=colvec,pch=pchvec,cex=0.8)
        if(leg && nmethod==5) legend(0.4,1.05,legend=c("EM-Tr","EM-Ra","EM-TO","TCA","MICS"),
                       col=colvec,pch=pchvec,cex=0.8)
        if(leg && nmethod==4) legend(0.4,0.42,legend=c("EM-Tr","EM-TO","TCA","MICS"),
                       col=colvec,pch=pchvec,cex=0.8)

        return(myplot)
}

powerplot <- function(Nsam,Ncell,tabmat,nmethod=6,
                      text=FALSE,ylab=FALSE,xlab=FALSE,yax=FALSE,title=FALSE){
        colvec <- c("#E69F00", "#56B4E9", "#009E73", 
                       "#0072B2", "#D55E00", "#CC79A7") #colorblind friendly
        pchvec <- 0:5
        ind <- matrix(c(1,1,1+nmethod,2,1+(2*nmethod),3,1+(3*nmethod),4),
                      nrow=4,ncol=2,byrow=TRUE)
        y.add <- ifelse(Nsam==1000,Ncell*2,ifelse(Nsam==500,Ncell,0))
        plotvec <- c()
        for(i in 1:Ncell){
                plotvec <- cbind(plotvec,
                      tabmat[ind[i,1],ind[i,2]+y.add])
        }
        myplot <- plot(as.vector(plotvec),type="b",xlim=c(0.5,Ncell+0.5),
             ylim=c(0,100),col=colvec[1],pch=pchvec[1],
             xlab="",
             ylab="",xaxt="n",yaxt="n")
        if(text && nmethod==6) legend(0.4,105,legend=c("EM-Tr","EM-Ra","EM-H","EM-TO",
                                                       "TCA","MICS"),
                       col=colvec,pch=pchvec,cex=0.8)
        for(i in 1:5){
                plotvec2 <- c() 
                        for(j in 1:Ncell){
                                plotvec2 <- cbind(plotvec2,
                                tabmat[ind[j,1]+i,ind[j,2]+y.add])
                        }
                lines(as.vector(plotvec2),
                      type="b",col=colvec[i+1],pch=pchvec[i+1])
                # if (text) text(c(0.7,0.7,0.8,0.8,0.8)[i],c(96, 55,45,12,3)[i],str_replace_all(substr(rownames(tabmat)[i+1],1,7)," ",""))
        }
        axis(1,at=1:Ncell,labels = TRUE,tck=0,padj=-1.8)
        if(yax) axis(2,at=c(0,25,50,75,100),labels = TRUE,tck=0,las=2, mgp=c(3, .2, 0))
        if(ylab) title(ylab="Power", line=1)
        if(xlab) title(xlab="Mediating Cell", line=1)
        mymain <- ifelse(Nsam==200,"N=200",ifelse(Nsam==500,"N=500","N=1000"))
        if(title) title(main=mymain,line=0.2,font.main=1)
        return(myplot)
}

linesep<-function(x,y=character()){
  if(!length(x))
    return(y)
  linesep(x[-length(x)], c(rep('',x[length(x)]-1),'\\addlinespace',y))  
}


# tabmat.2cells <- cbind(gettabmat(200,2),gettabmat(500,2),gettabmat(1000,2))
# tabmat.3cells <- cbind(gettabmat(200,3),gettabmat(500,3),gettabmat(1000,3))
# tabmat.4cells <- cbind(gettabmat(200,4),gettabmat(500,4),gettabmat(1000,4))

myrows <- c("EM - True","EM - Random","EM - Hybrid","EM - TOAST",
                             "TCA","MICS",
                             "EM - True ","EM - Random ","EM - Hybrid ","EM - TOAST ",
                             "TCA ","MICS ",
                             "EM - True  ","EM - Random  ","EM - Hybrid  ","EM - TOAST  ",
                             "TCA  ","MICS  ",
                             "EM - True   ","EM - Random   ","EM - Hybrid   ","EM - TOAST   ",
                             "TCA   ","MICS   ",
                             "EM - True    ","EM - Random    ","EM - Hybrid    ",
                              "EM - TOAST    ",
                             "TCA    ","MICS    ",
                             "EM - True     ","EM - Random     ","EM - Hybrid     ",
                              "EM - TOAST     ",
                             "TCA     ","MICS     ",
                             "EM - True      ","EM - Random      ","EM - Hybrid      ",
                              "EM - TOAST      ",
                             "TCA      ","MICS      ",
                             "EM - True       ","EM - Random       ","EM - Hybrid       ",
                              "EM - TOAST       ",
                             "TCA       ","MICS       ")
# rownames(tabmat.2cells) <- myrows[1:12]
# rownames(tabmat.3cells) <- myrows[1:18]
# rownames(tabmat.4cells) <- myrows[1:24]


gettabmat2 <- function(Ncell,noise1,noise2){
  sam <- c(200,500,1000)
  methods <- c("EM_truePvals","EM_randPvals","EM_hybridPvals","EM_toastPvals","TCA_Pvals","MICS_Pvals")
  mymat <- matrix(NA,nrow=Ncell*length(methods),ncol=Ncell*length(sam))
  for(k in sam){
    for(i in 1:Ncell){
      for(j in methods){
        mymat[seq(which(methods==j),Ncell*length(methods),length(methods))[i],(which(sam==k)*Ncell-(Ncell-1)):(Ncell*which(sam==k))] <- colSums(getpvalmat("050521",Ncell,i,k,
                                         j,noise1,noise1,noise2,alpha=0.05/Ncell)$binmat)
      }
    }
  }
  return(mymat)
}
```

<!-- \newpage -->
<!-- \section{Tables} -->

```{r newtabs, echo=FALSE, eval=FALSE}
tabmat2 <- rbind(gettabmat2(2,0.03,5),gettabmat2(2,0.1,2))
rownames(tabmat2) <- myrows[1:nrow(tabmat2)]

kable(tabmat2,caption="Significant cell types out of 100 replicates - 2 cells (.4, .6)",col.names=c("Cell 1","Cell 2","Cell 1","Cell 2","Cell 1","Cell 2"),booktabs=T)%>% 
        kable_styling(latex_options = c("hold_position")) %>% 
        column_spec(c(2,4,6), bold = c(T,T,T,T,T,T,F,F,F,F,F,F,T,T,T,T,T,T,F,F,F,F,F,F))%>% 
        column_spec(c(3,5,7), bold = c(F,F,F,F,F,F,T,T,T,T,T,T,F,F,F,F,F,F,T,T,T,T,T,T))%>%
        add_header_above(c(" "=1,"N=200"=2,"N=500"=2,"N=1000"=2)) %>% 
        pack_rows("Low noise (sigma=0.03, gamma=0.004)", 1, 12) %>% 
        pack_rows("High noise (sigma=0.1, gamma=0.01)", 13, 24)

tabmat3 <- rbind(gettabmat2(3,0.03,5),gettabmat2(3,0.1,2))
rownames(tabmat3) <- myrows[1:nrow(tabmat3)]
kable(tabmat3,caption="Significant cell types out of 100 replicates - 3 cells (.2, .3, .5)",col.names=c("Cell 1","Cell 2","Cell 3","Cell 1","Cell 2","Cell 3","Cell 1","Cell 2","Cell 3"),booktabs=T)%>%
        kable_styling(latex_options = c("hold_position")) %>%
        column_spec(c(2,5,8), bold = c(T,T,T,T,T,T,F,F,F,F,F,F,F,F,F,F,F,F,
                                       T,T,T,T,T,T,F,F,F,F,F,F,F,F,F,F,F,F))%>%
        column_spec(c(3,6,9), bold = c(F,F,F,F,F,F,T,T,T,T,T,T,F,F,F,F,F,F,
                                       F,F,F,F,F,F,T,T,T,T,T,T,F,F,F,F,F,F))%>%
        column_spec(c(4,7,10), bold = c(F,F,F,F,F,F,F,F,F,F,F,F,T,T,T,T,T,T,
                                        F,F,F,F,F,F,F,F,F,F,F,F,T,T,T,T,T,T))%>%
        add_header_above(c(" "=1,"N=200"=3,"N=500"=3,"N=1000"=3)) %>%
        pack_rows("Low noise (sigma=0.03, gamma=0.004)", 1, 18) %>%
        pack_rows("High noise (sigma=0.1, gamma=0.01)", 19, 36)

```


```{r newtabs2, echo=FALSE, eval=FALSE}
tabmat4 <- rbind(gettabmat2(4,0.03,5),gettabmat2(4,0.1,2))
rownames(tabmat4) <- myrows[1:nrow(tabmat4)]
kable(tabmat4,caption="Significant cell types out of 100 replicates - 4 cells (.1, .2, .3, .4)",col.names=c("Cell 1","Cell 2","Cell 3","Cell 4","Cell 1","Cell 2","Cell 3","Cell 4","Cell 1","Cell 2","Cell 3","Cell 4"),booktabs=T)%>% 
        kable_styling(latex_options = c("hold_position")) %>% 
        column_spec(c(2,6,10), bold = c(T,T,T,T,T,T,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,
                                        T,T,T,T,T,T,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F))%>%
        column_spec(c(3,7,11), bold = c(F,F,F,F,F,F,T,T,T,T,T,T,F,F,F,F,F,F,F,F,F,F,F,F,
                                        F,F,F,F,F,F,T,T,T,T,T,T,F,F,F,F,F,F,F,F,F,F,F,F))%>%
        column_spec(c(4,8,12), bold = c(F,F,F,F,F,F,F,F,F,F,F,F,T,T,T,T,T,T,F,F,F,F,F,F,
                                        F,F,F,F,F,F,F,F,F,F,F,F,T,T,T,T,T,T,F,F,F,F,F,F))%>%
        column_spec(c(5,9,13), bold = c(F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,T,T,T,T,T,T,
                                        F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,F,T,T,T,T,T,T))%>%
        add_header_above(c(" "=1,"N=200"=4,"N=500"=4,"N=1000"=4)) %>% 
        pack_rows("High noise (sigma=0.1, gamma=0.01)", 1, 24) %>% 
        pack_rows("High noise (sigma=0.1, gamma=0.01)", 25, 48)

```

<!-- \clearpage -->
<!-- \section{Plots} -->



```{r type1plot, echo=FALSE, results='hide', eval=FALSE}

tab.2 <- rbind(tabmat2[1:6,c(2,4,6)],
               setNames(tabmat2[7:12,c(1,3,5)], names(tabmat2[7:12,c(2,4,6)])))/100
tab.3 <- type1tab(tabmat3[1:18,],6)
tab.4 <- type1tab(tabmat4[1:24,],6)

par(mfrow=c(3,3), mai=c(0.3,0.3,0.15,0))
type1plot(200,2,tab.2,ylab=TRUE,yax=TRUE,text=TRUE,title=TRUE,leg=TRUE)
type1plot(500,2,tab.2,title=TRUE)
type1plot(1000,2,tab.2,title=TRUE)
type1plot(200,3,tab.3,yax=TRUE,ylab=TRUE)
type1plot(500,3,tab.3)
type1plot(1000,3,tab.3)
type1plot(200,4,tab.4,xlab=TRUE,yax=TRUE,ylab=TRUE)
type1plot(500,4,tab.4,xlab=TRUE)
type1plot(1000,4,tab.4,xlab=TRUE)


```
<!-- **Figure 1**: Type 1 error for all methods - low noise setting. For rows 2 and 3 (3 sites and 4 sites, respectively), the average of the type 1 error is plotted. For example, the leftmost point on the bottom left plot is the average number of replicates, across cell types 2, 3, and 4, (incorrectly) found to be significant. Note that only one cell type is a mediator at one time. -->

```{r type1plot22, echo=FALSE, results='hide', eval=FALSE}

tab.2a <- rbind(tabmat2[13:18,c(2,4,6)],
               setNames(tabmat2[19:24,c(1,3,5)], names(tabmat2[19:24,c(2,4,6)])))/100
tab.3a <- type1tab(tabmat3[19:36,],6)
tab.4a <- type1tab(tabmat4[25:48,],6)

par(mfrow=c(3,3), mai=c(0.3,0.3,0.15,0))
type1plot(200,2,tab.2a,ylab=TRUE,yax=TRUE,text=TRUE,title=TRUE,leg=TRUE)
type1plot(500,2,tab.2a,title=TRUE)
type1plot(1000,2,tab.2a,title=TRUE)
type1plot(200,3,tab.3a,yax=TRUE,ylab=TRUE)
type1plot(500,3,tab.3a)
type1plot(1000,3,tab.3a)
type1plot(200,4,tab.4a,xlab=TRUE,yax=TRUE,ylab=TRUE)
type1plot(500,4,tab.4a,xlab=TRUE)
type1plot(1000,4,tab.4a,xlab=TRUE)


```
<!-- **Figure 2**: Type 1 error for all methods - high noise setting. -->

```{r typ1plot2, echo=FALSE, results='hide', eval=FALSE}

tab.2a <- tab.2[-c(2,7),]
tab.3a <- tab.3[-c(2,7,12),]
tab.4a <- tab.4[-c(2,7,12,17),]

par(mfrow=c(3,3), mai=c(0.3,0.3,0.15,0))
type1plot(200,2,tab.2a,nmethod=4,ylab=TRUE,yax=TRUE,text=TRUE,title=TRUE,leg=TRUE)
type1plot(500,2,tab.2a,nmethod=4,title=TRUE)
type1plot(1000,2,tab.2a,nmethod=4,title=TRUE)
type1plot(200,3,tab.3a,nmethod=4,yax=TRUE,ylab=TRUE)
type1plot(500,3,tab.3a,nmethod=4,)
type1plot(1000,3,tab.3a,nmethod=4,)
type1plot(200,4,tab.4a,nmethod=4,xlab=TRUE,yax=TRUE,ylab=TRUE)
type1plot(500,4,tab.4a,nmethod=4,xlab=TRUE)
type1plot(1000,4,tab.4a,nmethod=4,xlab=TRUE)




```
<!-- **Figure 1B**: Type 1 error without EM - Random to better differentiate between the other methods. -->


```{r plots, echo=FALSE, results='hide', eval=FALSE}
tabmat2a <- tabmat2[1:12,]
tabmat3a <- tabmat3[1:18,]
tabmat4a <- tabmat4[1:24,]

par(mfrow=c(3,3), mai=c(0.3,0.3,0.15,0))
powerplot(200,2,tabmat2a,ylab=TRUE,yax=TRUE,text=TRUE,title=TRUE)
powerplot(500,2,tabmat2a,title=TRUE)
powerplot(1000,2,tabmat2a,title=TRUE)
powerplot(200,3,tabmat3a,yax=TRUE,ylab=TRUE)
powerplot(500,3,tabmat3a)
powerplot(1000,3,tabmat3a)
powerplot(200,4,tabmat4a,xlab=TRUE,yax=TRUE,ylab=TRUE)
powerplot(500,4,tabmat4a,xlab=TRUE)
powerplot(1000,4,tabmat4a,xlab=TRUE)

```
<!-- **Figure 3**: Power for all methods - low noise setting. The number plotted is the number of times, out of 100 replicates, that that cell type was correctly identified as a mediator. Note that only one cell type is a mediator at a time. -->

```{r plotsbbb, echo=FALSE, results='hide', eval=FALSE}
tabmat2b <- tabmat2[13:24,]
tabmat3b <- tabmat3[19:36,]
tabmat4b <- tabmat4[25:48,]

par(mfrow=c(3,3), mai=c(0.3,0.3,0.15,0))
powerplot(200,2,tabmat2b,ylab=TRUE,yax=TRUE,text=TRUE,title=TRUE)
powerplot(500,2,tabmat2b,title=TRUE)
powerplot(1000,2,tabmat2b,title=TRUE)
powerplot(200,3,tabmat3b,yax=TRUE,ylab=TRUE)
powerplot(500,3,tabmat3b)
powerplot(1000,3,tabmat3b)
powerplot(200,4,tabmat4b,xlab=TRUE,yax=TRUE,ylab=TRUE)
powerplot(500,4,tabmat4b,xlab=TRUE)
powerplot(1000,4,tabmat4b,xlab=TRUE)

```
<!-- **Figure 4**: Power for all methods - high noise setting. -->

\clearpage
\newpage

\section{ROC Curves}

To produce the ROC curves, I calculated a p-value for each method (rather than only a binary significance decision based on the bootstrap CI). For EM and TCA, to calculate the p-value, I took the minimum of (1) the number of bootstrap indirect effect estimates $>$ 0, and (2) the number of bootstrap indirect effect estimates $<$ 0, divided this number by the number of bootstrap samples, and multiplied by 2. I did not take the standard deviation of the bootstrap estimates and use that in a Wald test statistic because I did not want to assume normality of the distribution of the indirect effect. MICS gives p-values directly.

Each plot shows one site/cell-type scenario and compares the true positives of the mediating cell type in that scenario to the false negatives in the non-mediating cell type(s).

```{r 2cellROCsmallsd1, echo=FALSE, results='hide'}

par(mfrow=c(3,2), mai=c(0.1,0.1,0.1,0))
makeroc("052421",2,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("052421",2,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator",type="roc")
makeroc("052421",2,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator",type="roc")
makeroc("052421",2,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator",type="roc")
makeroc("052421",2,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator",type="roc")
makeroc("052421",2,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator",type="roc")


```
2 cell types, low noise (sigma=tau=0.03, gamma $\approx$ 0.004)

\newpage

```{r 2cellROCsmallsd1pr, echo=FALSE, results='hide'}

par(mfrow=c(3,2), mai=c(0.1,0.1,0.1,0))
makeroc("052421",2,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="pr")
makeroc("052421",2,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator",type="pr")
makeroc("052421",2,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator",type="pr")
makeroc("052421",2,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator",type="pr")
makeroc("052421",2,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator",type="pr")
makeroc("052421",2,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator",type="pr")


```
2 cell types, low noise (sigma=tau=0.03, gamma $\approx$ 0.004)

<!-- \newpage -->


```{r 3cellROCsmallsd1, echo=FALSE, results='hide'}
par(mfrow=c(3,3), mai=c(0.1,0.1,0.1,0))
makeroc("052421",3,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("052421",3,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator",type="roc")
makeroc("052421",3,3,200,0.03,0.03,gammadenom=5,title="N=200,cell 3 mediator",type="roc")
makeroc("052421",3,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator",type="roc")
makeroc("052421",3,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator",type="roc")
makeroc("052421",3,3,500,0.03,0.03,gammadenom=5,title="N=500,cell 3 mediator",type="roc")
makeroc("052421",3,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator",type="roc")
makeroc("052421",3,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator",type="roc")
makeroc("052421",3,3,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 3 mediator",type="roc")

```
3 cell types, low noise (sigma=tau=0.03, gamma $\approx$ 0.004)

\newpage

```{r 3cellROCsmallsd1pr, echo=FALSE, results='hide'}
par(mfrow=c(3,3), mai=c(0.1,0.1,0.1,0))
makeroc("052421",3,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="pr")
makeroc("052421",3,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator",type="pr")
makeroc("052421",3,3,200,0.03,0.03,gammadenom=5,title="N=200,cell 3 mediator",type="pr")
makeroc("052421",3,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator",type="pr")
makeroc("052421",3,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator",type="pr")
makeroc("052421",3,3,500,0.03,0.03,gammadenom=5,title="N=500,cell 3 mediator",type="pr")
makeroc("052421",3,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator",type="pr")
makeroc("052421",3,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator",type="pr")
makeroc("052421",3,3,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 3 mediator",type="pr")

```
3 cell types, low noise (sigma=tau=0.03, gamma $\approx$ 0.004)


```{r 4cellROCsmallsd1, echo=FALSE, results='hide'}
par(mfrow=c(3,4), mai=c(0.1,0.1,0.1,0))
makeroc("052421",4,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("052421",4,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator",type="roc")
makeroc("052421",4,3,200,0.03,0.03,gammadenom=5,title="N=200,cell 3 mediator",type="roc")
makeroc("052421",4,4,200,0.03,0.03,gammadenom=5,title="N=200,cell 4 mediator",type="roc")
makeroc("052421",4,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator",type="roc")
makeroc("052421",4,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator",type="roc")
makeroc("052421",4,3,500,0.03,0.03,gammadenom=5,title="N=500,cell 3 mediator",type="roc")
makeroc("052421",4,4,500,0.03,0.03,gammadenom=5,title="N=500,cell 4 mediator",type="roc")
makeroc("052421",4,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator",type="roc")
makeroc("052421",4,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator",type="roc")
makeroc("052421",4,3,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 3 mediator",type="roc")
makeroc("052421",4,4,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 4 mediator",type="roc")

```
4 cell types, low noise (sigma=tau=0.03, gamma $\approx$ 0.004)

```{r 4cellROCsmallsd1ex, echo=FALSE, results='hide'}
par(mfrow=c(3,4), mai=c(0.1,0.1,0.1,0))
makeroc("060921",4,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("060921",4,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator",type="roc")
makeroc("060921",4,3,200,0.03,0.03,gammadenom=5,title="N=200,cell 3 mediator",type="roc")
makeroc("060921",4,4,200,0.03,0.03,gammadenom=5,title="N=200,cell 4 mediator",type="roc")
makeroc("060921",4,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator",type="roc")
makeroc("060921",4,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator",type="roc")
makeroc("060921",4,3,500,0.03,0.03,gammadenom=5,title="N=500,cell 3 mediator",type="roc")
makeroc("060921",4,4,500,0.03,0.03,gammadenom=5,title="N=500,cell 4 mediator",type="roc")
makeroc("060921",4,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator",type="roc")
makeroc("060921",4,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator",type="roc")
makeroc("060921",4,3,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 3 mediator",type="roc")
makeroc("060921",4,4,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 4 mediator",type="roc")

```
4 cell types, low noise (sigma=tau=0.03, gamma $\approx$ 0.004), extreme cell proportions (0.49 - 0.49 - 0.01 - 0.01)

```{r 4cellROCsmallsd1ex2, echo=FALSE, results='hide'}
par(mfrow=c(3,4), mai=c(0.1,0.1,0.1,0))
makeroc("062121",4,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("062121",4,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator",type="roc")
makeroc("062121",4,3,200,0.03,0.03,gammadenom=5,title="N=200,cell 3 mediator",type="roc")
makeroc("062121",4,4,200,0.03,0.03,gammadenom=5,title="N=200,cell 4 mediator",type="roc")
makeroc("062121",4,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator",type="roc")
makeroc("062121",4,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator",type="roc")
makeroc("062121",4,3,500,0.03,0.03,gammadenom=5,title="N=500,cell 3 mediator",type="roc")
makeroc("062121",4,4,500,0.03,0.03,gammadenom=5,title="N=500,cell 4 mediator",type="roc")
makeroc("062121",4,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator",type="roc")
makeroc("062121",4,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator",type="roc")
makeroc("062121",4,3,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 3 mediator",type="roc")
makeroc("062121",4,4,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 4 mediator",type="roc")

```
4 cell types, low noise (sigma=tau=0.03, gamma $\approx$ 0.004), extreme cell proportions (0.01 - 0.49 - 0.49 - 0.01)

\newpage

```{r 4cellROCsmallsd1ex3, echo=FALSE, results='hide'}
par(mfrow=c(3,4), mai=c(0.1,0.1,0.1,0))
makeroc("062121a",4,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("062121a",4,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator",type="roc")
makeroc("062121a",4,3,200,0.03,0.03,gammadenom=5,title="N=200,cell 3 mediator",type="roc")
makeroc("062121a",4,4,200,0.03,0.03,gammadenom=5,title="N=200,cell 4 mediator",type="roc")
makeroc("062121a",4,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator",type="roc")
makeroc("062121a",4,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator",type="roc")
makeroc("062121a",4,3,500,0.03,0.03,gammadenom=5,title="N=500,cell 3 mediator",type="roc")
makeroc("062121a",4,4,500,0.03,0.03,gammadenom=5,title="N=500,cell 4 mediator",type="roc")
makeroc("062121a",4,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator",type="roc")
makeroc("062121a",4,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator",type="roc")
makeroc("062121a",4,3,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 3 mediator",type="roc")
makeroc("062121a",4,4,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 4 mediator",type="roc")

```
4 cell types, low noise (sigma=tau=0.03, gamma $\approx$ 0.004), extreme cell proportions (0.97 - 0.01 - 0.01 - 0.01)

\newpage

```{r 4cellROCsmallsd1ex4, echo=FALSE, results='hide'}
par(mfrow=c(3,4), mai=c(0.1,0.1,0.1,0))
makeroc("062121a",4,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="roc",nmethod=5)
makeroc("062121a",4,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator",type="roc",nmethod=5)
makeroc("062121a",4,3,200,0.03,0.03,gammadenom=5,title="N=200,cell 3 mediator",type="roc",nmethod=5)
makeroc("062121a",4,4,200,0.03,0.03,gammadenom=5,title="N=200,cell 4 mediator",type="roc",nmethod=5)
makeroc("062121a",4,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator",type="roc",nmethod=5)
makeroc("062121a",4,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator",type="roc",nmethod=5)
makeroc("062121a",4,3,500,0.03,0.03,gammadenom=5,title="N=500,cell 3 mediator",type="roc",nmethod=5)
makeroc("062121a",4,4,500,0.03,0.03,gammadenom=5,title="N=500,cell 4 mediator",type="roc",nmethod=5)
makeroc("062121a",4,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator",type="roc",nmethod=5)
makeroc("062121a",4,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator",type="roc",nmethod=5)
makeroc("062121a",4,3,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 3 mediator",type="roc",nmethod=5)
makeroc("062121a",4,4,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 4 mediator",type="roc",nmethod=5)

```
4 cell types, low noise (sigma=tau=0.03, gamma $\approx$ 0.004), extreme cell proportions (0.97 - 0.01 - 0.01 - 0.01)

\newpage

```{r 2cellcompare, echo=FALSE, results='hide'}
par(mfrow=c(4,2), mai=c(0.1,0.1,0.1,0))
makeroc("071921_9901",2,1,1000,0.03,0.03,gammadenom=5,leg=TRUE,title="0.99",type="roc",nmethod=3)
makeroc("071921_9901",2,2,1000,0.03,0.03,gammadenom=5,title="0.01",type="roc",nmethod=3)
makeroc("071921_9010",2,1,1000,0.03,0.03,gammadenom=5,title="0.9",type="roc",nmethod=3)
makeroc("071921_9010",2,2,1000,0.03,0.03,gammadenom=5,title="0.1",type="roc",nmethod=3)
makeroc("071921_7030",2,1,1000,0.03,0.03,gammadenom=5,title="0.7",type="roc",nmethod=3)
makeroc("071921_7030",2,2,1000,0.03,0.03,gammadenom=5,title="0.3",type="roc",nmethod=3)
makeroc("071921_5050",2,1,1000,0.03,0.03,gammadenom=5,title="0.5",type="roc",nmethod=3)
makeroc("071921_5050",2,2,1000,0.03,0.03,gammadenom=5,title="0.5",type="roc",nmethod=3)

```
2 cell types, cell type proportion comparison

\newpage

```{r 4cellROCsmallsd1pr, echo=FALSE, results='hide'}
par(mfrow=c(3,4), mai=c(0.1,0.1,0.1,0))
makeroc("052421",4,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="pr")
makeroc("052421",4,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator",type="pr")
makeroc("052421",4,3,200,0.03,0.03,gammadenom=5,title="N=200,cell 3 mediator",type="pr")
makeroc("052421",4,4,200,0.03,0.03,gammadenom=5,title="N=200,cell 4 mediator",type="pr")
makeroc("052421",4,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator",type="pr")
makeroc("052421",4,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator",type="pr")
makeroc("052421",4,3,500,0.03,0.03,gammadenom=5,title="N=500,cell 3 mediator",type="pr")
makeroc("052421",4,4,500,0.03,0.03,gammadenom=5,title="N=500,cell 4 mediator",type="pr")
makeroc("052421",4,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator",type="pr")
makeroc("052421",4,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator",type="pr")
makeroc("052421",4,3,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 3 mediator",type="pr")
makeroc("052421",4,4,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 4 mediator",type="pr")

```
4 cell types, low noise (sigma=tau=0.03, gamma $\approx$ 0.004)


\newpage

```{r 2cellROCsmallsd2, echo=FALSE, results='hide'}

par(mfrow=c(3,2), mai=c(0.1,0.1,0.1,0))
makeroc("052421",2,1,200,0.06,0.06,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("052421",2,2,200,0.06,0.06,title="N=200,cell 2 mediator",type="roc")
makeroc("052421",2,1,500,0.06,0.06,title="N=500,cell 1 mediator",type="roc")
makeroc("052421",2,2,500,0.06,0.06,title="N=500,cell 2 mediator",type="roc")
makeroc("052421",2,1,1000,0.06,0.06,title="N=1000,cell 1 mediator",type="roc")
makeroc("052421",2,2,1000,0.06,0.06,title="N=1000,cell 2 mediator",type="roc")


```
2 cell types, High noise (sigma=tau=0.06, gamma $\approx$ 0.01)

\newpage


```{r 3cellROCsmallsd2, echo=FALSE, results='hide'}
par(mfrow=c(3,3), mai=c(0.1,0.1,0.1,0))
makeroc("052421",3,1,200,0.06,0.06,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("052421",3,2,200,0.06,0.06,title="N=200,cell 2 mediator",type="roc")
makeroc("052421",3,3,200,0.06,0.06,title="N=200,cell 3 mediator",type="roc")
makeroc("052421",3,1,500,0.06,0.06,title="N=500,cell 1 mediator",type="roc")
makeroc("052421",3,2,500,0.06,0.06,title="N=500,cell 2 mediator",type="roc")
makeroc("052421",3,3,500,0.06,0.06,title="N=500,cell 3 mediator",type="roc")
makeroc("052421",3,1,1000,0.06,0.06,title="N=1000,cell 1 mediator",type="roc")
makeroc("052421",3,2,1000,0.06,0.06,title="N=1000,cell 2 mediator",type="roc")
makeroc("052421",3,3,1000,0.06,0.06,title="N=1000,cell 3 mediator",type="roc")

```
3 cell types, High noise (sigma=tau=0.06, gamma $\approx$ 0.01)


```{r 4cellROCsmallsd2, echo=FALSE, results='hide'}
par(mfrow=c(3,4), mai=c(0.1,0.1,0.1,0))
makeroc("052421",4,1,200,0.06,0.06,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("052421",4,2,200,0.06,0.06,title="N=200,cell 2 mediator",type="roc")
makeroc("052421",4,3,200,0.06,0.06,title="N=200,cell 3 mediator",type="roc")
makeroc("052421",4,4,200,0.06,0.06,title="N=200,cell 4 mediator",type="roc")
makeroc("052421",4,1,500,0.06,0.06,title="N=500,cell 1 mediator",type="roc")
makeroc("052421",4,2,500,0.06,0.06,title="N=500,cell 2 mediator",type="roc")
makeroc("052421",4,3,500,0.06,0.06,title="N=500,cell 3 mediator",type="roc")
makeroc("052421",4,4,500,0.06,0.06,title="N=500,cell 4 mediator",type="roc")
makeroc("052421",4,1,1000,0.06,0.06,title="N=1000,cell 1 mediator",type="roc")
makeroc("052421",4,2,1000,0.06,0.06,title="N=1000,cell 2 mediator",type="roc")
makeroc("052421",4,3,1000,0.06,0.06,title="N=1000,cell 3 mediator",type="roc")
makeroc("052421",4,4,1000,0.06,0.06,title="N=1000,cell 4 mediator",type="roc")

```
4 cell types, High noise (sigma=tau=0.06, gamma $\approx$ 0.01)

\newpage

```{r 2cellROCsmallsd2m, echo=FALSE, results='hide'}

par(mfrow=c(3,2), mai=c(0.1,0.1,0.1,0))
makeroc("052421",2,1,200,0.06,0.06,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("052421",2,2,200,0.06,0.06,gammadenom=5,title="N=200,cell 2 mediator",type="roc")
makeroc("052421",2,1,500,0.06,0.06,gammadenom=5,title="N=500,cell 1 mediator",type="roc")
makeroc("052421",2,2,500,0.06,0.06,gammadenom=5,title="N=500,cell 2 mediator",type="roc")
makeroc("052421",2,1,1000,0.06,0.06,gammadenom=5,title="N=1000,cell 1 mediator",type="roc")
makeroc("052421",2,2,1000,0.06,0.06,gammadenom=5,title="N=1000,cell 2 mediator",type="roc")


```
2 cell types, Mixed noise (sigma=tau=0.06, gamma $\approx$ 0.004)

\newpage


```{r 3cellROCsmallsd2m, echo=FALSE, results='hide',eval=FALSE}
par(mfrow=c(3,3), mai=c(0.1,0.1,0.1,0))
makeroc("052421",3,1,200,0.06,0.06,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("052421",3,2,200,0.06,0.06,gammadenom=5,title="N=200,cell 2 mediator",type="roc")
makeroc("052421",3,3,200,0.06,0.06,gammadenom=5,title="N=200,cell 3 mediator",type="roc")
makeroc("052421",3,1,500,0.06,0.06,gammadenom=5,title="N=500,cell 1 mediator",type="roc")
makeroc("052421",3,2,500,0.06,0.06,gammadenom=5,title="N=500,cell 2 mediator",type="roc")
makeroc("052421",3,3,500,0.06,0.06,gammadenom=5,title="N=500,cell 3 mediator",type="roc")
makeroc("052421",3,1,1000,0.06,0.06,gammadenom=5,title="N=1000,cell 1 mediator",type="roc")
makeroc("052421",3,2,1000,0.06,0.06,gammadenom=5,title="N=1000,cell 2 mediator",type="roc")
makeroc("052421",3,3,1000,0.06,0.06,gammadenom=5,title="N=1000,cell 3 mediator",type="roc")

```
<!-- 3 cell types, Mixed noise (sigma=tau=0.06, gamma $\approx$ 0.004) -->


```{r 4cellROCsmallsd2m, echo=FALSE, results='hide'}
par(mfrow=c(3,4), mai=c(0.1,0.1,0.1,0))
makeroc("052421",4,1,200,0.06,0.06,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator",type="roc")
makeroc("052421",4,2,200,0.06,0.06,gammadenom=5,title="N=200,cell 2 mediator",type="roc")
makeroc("052421",4,3,200,0.06,0.06,gammadenom=5,title="N=200,cell 3 mediator",type="roc")
makeroc("052421",4,4,200,0.06,0.06,gammadenom=5,title="N=200,cell 4 mediator",type="roc")
makeroc("052421",4,1,500,0.06,0.06,gammadenom=5,title="N=500,cell 1 mediator",type="roc")
makeroc("052421",4,2,500,0.06,0.06,gammadenom=5,title="N=500,cell 2 mediator",type="roc")
makeroc("052421",4,3,500,0.06,0.06,gammadenom=5,title="N=500,cell 3 mediator",type="roc")
makeroc("052421",4,4,500,0.06,0.06,gammadenom=5,title="N=500,cell 4 mediator",type="roc")
makeroc("052421",4,1,1000,0.06,0.06,gammadenom=5,title="N=1000,cell 1 mediator",type="roc")
makeroc("052421",4,2,1000,0.06,0.06,gammadenom=5,title="N=1000,cell 2 mediator",type="roc")
makeroc("052421",4,3,1000,0.06,0.06,gammadenom=5,title="N=1000,cell 3 mediator",type="roc")
makeroc("052421",4,4,1000,0.06,0.06,gammadenom=5,title="N=1000,cell 4 mediator",type="roc")

```
4 cell types, Mixed noise (sigma=tau=0.06, gamma $\approx$ 0.004)

\section{Real Data}

 - smoking status, weight
 - N=683
 - 6 cell types: 195 sites using 1e-10 p-value threshold
 - 4 cell types: 151 sites using 1e-5 p-value threshold

```{r realdattab, echo=FALSE}

mat4cell <- colSums(ifelse(read.table("Pvals116sites")==0,1,0))
mat4cellprop <- round(c(0.55582288, 0.27177197, 0.08003587, 0.06055624),2)
mat6cellprop <- round(c(0.10844789,0.17434936,0.05178539,0.06825377,0.08419534,0.51296825),2)
mat6cell <- colSums(ifelse(rbind(read.table("Pvals6cells_1_50"),read.table("Pvals6cells_51_100"),read.table("Pvals6cells_101_150"),read.table("Pvals6cells_151_195"))==0,1,0))

mat4 <- rbind(mat4cellprop,mat4cell)
mat6 <- rbind(mat6cellprop,mat6cell)

rownames(mat4) <- rownames(mat6) <- c("Mean cell proportions","Number of significant sites")

kable(mat4,caption="4 cell types (151 sites)",col.names=c("Cell 1","Cell 2","Cell 3","Cell 4"),booktabs=T)%>% 
        kable_styling(latex_options = c("hold_position"))

kable(mat6,caption="6 cell types (195 sites)",
      col.names=c("CD8T","CD4T","NK","Bcell","Mono","Neu"),booktabs=T)%>% 
        kable_styling(latex_options = c("hold_position"))

```

\section{Previous results for reference}

```{r 2cellROCsmallsd, echo=FALSE, results='hide'}

par(mfrow=c(3,2), mai=c(0.1,0.1,0.1,0))
makeroc("050521",2,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator")
makeroc("050521",2,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator")
makeroc("050521",2,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator")
makeroc("050521",2,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator")
makeroc("050521",2,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator")
makeroc("050521",2,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator")


```
2 cell types, Low noise (sigma=tau=0.03, gamma $\approx$ 0.004)

\newpage

```{r 2cellROCbigsd, echo=FALSE, results='hide'}

par(mfrow=c(3,2), mai=c(0.1,0.1,0.1,0))
makeroc("050521",2,1,200,0.1,0.1,leg=TRUE,title="N=200,cell 1 mediator")
makeroc("050521",2,2,200,0.1,0.1,title="N=200,cell 2 mediator")
makeroc("050521",2,1,500,0.1,0.1,title="N=500,cell 1 mediator")
makeroc("050521",2,2,500,0.1,0.1,title="N=500,cell 2 mediator")
makeroc("050521",2,1,1000,0.1,0.1,title="N=1000,cell 1 mediator")
makeroc("050521",2,2,1000,0.1,0.1,title="N=1000,cell 2 mediator")

```
2 cell types, High noise (sigma=tau=0.1, gamma $\approx$ 0.01)


```{r 3cellROCsmallsd, echo=FALSE, results='hide'}
par(mfrow=c(3,3), mai=c(0.1,0.1,0.1,0))
makeroc("050521",3,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator")
makeroc("050521",3,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator")
makeroc("050521",3,3,200,0.03,0.03,gammadenom=5,title="N=200,cell 3 mediator")
makeroc("050521",3,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator")
makeroc("050521",3,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator")
makeroc("050521",3,3,500,0.03,0.03,gammadenom=5,title="N=500,cell 3 mediator")
makeroc("050521",3,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator")
makeroc("050521",3,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator")
makeroc("050521",3,3,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 3 mediator")

```
3 cell types, Low noise (sigma=tau=0.03, gamma $\approx$ 0.004)

```{r 3cellROCbigsd, echo=FALSE, results='hide'}
par(mfrow=c(3,3), mai=c(0.1,0.1,0.1,0))
makeroc("050521",3,1,200,0.1,0.1,leg=TRUE,title="N=200,cell 1 mediator")
makeroc("050521",3,2,200,0.1,0.1,title="N=200,cell 2 mediator")
makeroc("050521",3,3,200,0.1,0.1,title="N=200,cell 3 mediator")
makeroc("050521",3,1,500,0.1,0.1,title="N=500,cell 1 mediator")
makeroc("050521",3,2,500,0.1,0.1,title="N=500,cell 2 mediator")
makeroc("050521",3,3,500,0.1,0.1,title="N=500,cell 3 mediator")
makeroc("050521",3,1,1000,0.1,0.1,title="N=1000,cell 1 mediator")
makeroc("050521",3,2,1000,0.1,0.1,title="N=1000,cell 2 mediator")
makeroc("050521",3,3,1000,0.1,0.1,title="N=1000,cell 3 mediator")

```
3 cell types, High noise (sigma=tau=0.1, gamma $\approx$ 0.01)


```{r 4cellROCsmallsd, echo=FALSE, results='hide'}
par(mfrow=c(3,4), mai=c(0.1,0.1,0.1,0))
makeroc("050521",4,1,200,0.03,0.03,gammadenom=5,leg=TRUE,title="N=200,cell 1 mediator")
makeroc("050521",4,2,200,0.03,0.03,gammadenom=5,title="N=200,cell 2 mediator")
makeroc("050521",4,3,200,0.03,0.03,gammadenom=5,title="N=200,cell 3 mediator")
makeroc("050521",4,4,200,0.03,0.03,gammadenom=5,title="N=200,cell 4 mediator")
makeroc("050521",4,1,500,0.03,0.03,gammadenom=5,title="N=500,cell 1 mediator")
makeroc("050521",4,2,500,0.03,0.03,gammadenom=5,title="N=500,cell 2 mediator")
makeroc("050521",4,3,500,0.03,0.03,gammadenom=5,title="N=500,cell 3 mediator")
makeroc("050521",4,4,500,0.03,0.03,gammadenom=5,title="N=500,cell 4 mediator")
makeroc("050521",4,1,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 1 mediator")
makeroc("050521",4,2,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 2 mediator")
makeroc("050521",4,3,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 3 mediator")
makeroc("050521",4,4,1000,0.03,0.03,gammadenom=5,title="N=1000,cell 4 mediator")

```
4 cell types, Low noise (sigma=tau=0.03, gamma $\approx$ 0.004)


```{r 4cellROCbigsd, echo=FALSE, results='hide'}
par(mfrow=c(3,4), mai=c(0.1,0.1,0.1,0))
makeroc("050521",4,1,200,0.1,0.1,leg=TRUE,title="N=200,cell 1 mediator")
makeroc("050521",4,2,200,0.1,0.1,title="N=200,cell 2 mediator")
makeroc("050521",4,3,200,0.1,0.1,title="N=200,cell 3 mediator")
makeroc("050521",4,4,200,0.1,0.1,title="N=200,cell 4 mediator")
makeroc("050521",4,1,500,0.1,0.1,title="N=500,cell 1 mediator")
makeroc("050521",4,2,500,0.1,0.1,title="N=500,cell 2 mediator")
makeroc("050521",4,3,500,0.1,0.1,title="N=500,cell 3 mediator")
makeroc("050521",4,4,500,0.1,0.1,title="N=500,cell 4 mediator")
makeroc("050521",4,1,1000,0.1,0.1,title="N=1000,cell 1 mediator")
makeroc("050521",4,2,1000,0.1,0.1,title="N=1000,cell 2 mediator")
makeroc("050521",4,3,1000,0.1,0.1,title="N=1000,cell 3 mediator")
makeroc("050521",4,4,1000,0.1,0.1,title="N=1000,cell 4 mediator")

```
4 cell types, High noise (sigma=tau=0.1, gamma $\approx$ 0.01)



